Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-20 bdcloud_paper/latex/paper.tex
Added references

\section{Introduction}
Big data applications process large, continuously-changing data sets with the general goal of information and knowledge extraction.  New tools such as Hive, Pig and Crunch \textcolor{red}{reference} based around big data frameworks such as Hadoop, Storm, and Spark \textcolor{red}{reference} are being released every day. Development, testing and benchmarking of big data software, algorithms, and infrastructure pose unique challenges.  Though software and algorithms will be deployed to large clusters for benchmarking and production usage, engineers develop and test these tools on desktops due to the speed and ease of development and debugging on a local machine and limited access to large clusters due to the high costs of purchasing, provisioning, and maintaining such clusters.  Software and algorithms are being developed at incredible speed with new releases everyday. The high speed of development driven by the need to be the first to market in a competitive field often results in buggy software.  There is great need for consistent and rigorous testing and benchmarking frameworks to aid in the identification of bugs while maintaining the high-speed of development.  Access to high-quality, semantically-rich data sets and complex, realistic analytics workflow examples that can scale from local development environments to large clusters are key to increasing access to and development of consistent and rigorous testing and benchmarking frameworks.

>>>>

\section{Introduction}
Big data applications process large, continuously-changing data sets with the general goal of information and knowledge extraction.  New tools such as Hive \cite{Thusoo2010}, Pig \cite{Olston2008,Gates2009}, and Shark \cite{Engle2012} based around big data frameworks such as Hadoop \cite{Hadoop}, Storm \cite{Storm}, and Spark \cite{Zaharia2010,Zaharia2012} are being released every day. Development, testing and benchmarking of big data software, algorithms, and infrastructure pose unique challenges.  Though software and algorithms will be deployed to large clusters for benchmarking and production usage, engineers develop and test these tools on desktops due to the speed and ease of development and debugging on a local machine and limited access to large clusters due to the high costs of purchasing, provisioning, and maintaining such clusters.  Software and algorithms are being developed at incredible speed with new releases everyday. The high speed of development driven by the need to be the first to market in a competitive field often results in buggy software.  There is great need for consistent and rigorous testing and benchmarking frameworks to aid in the identification of bugs while maintaining the high-speed of development.  Access to high-quality, semantically-rich data sets and complex, realistic analytics workflow examples that can scale from local development environments to large clusters are key to increasing access to and development of consistent and rigorous testing and benchmarking frameworks.
